Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-03 article.tex
Fix abstract acronyms

\usepackage{acronym}
\acrodef{CRN}[CRN]{chemical reaction network}
\acrodef{DSL}[DSL]{domain-specific language}
\acrodef{GPU}[GPU]{graphical processing unit}
\acrodef{GUI}[GUI]{graphical user interface}
\acrodef{IDE}[IDE]{integrated development environment}
\acrodef{JIT}[JIT]{just-in-time}
\acrodef{ODE}[ODE]{ordinary differential equation}
\acrodef{PyPI}[PyPI]{Python package index}
\acrodef{RHS}[RHS]{right-hand side}
\acrodef{SBML}[SBML]{System Biology Markup Language}
\acrodef{SDE}[SDE]{stochastic differential equation}
\acrodef{TPU}[TPU]{tensor processing unit}

@@

\begin{abstract}
\Acf{CRN} play a pivotal role in diverse fields
such as systems biology, biochemistry, chemical engineering, and
epidemiology. High-level modelling of \acp{CRN} enables various simulation
approaches, including deterministic and stochastic methods. However,
existing Python tools for \ac{CRN} modelling typically wrap external C/C++
libraries for modelling and simulation, limiting their extensibility and
integration with the broader Python ecosystem. In response, we developed
Poincaré and SimBio, two novel Python packages for the definition and
simulation of dynamical systems and \acp{CRN}. Poincaré serves as a
foundation for dynamical system modelling, while SimBio extends this
functionality to \acp{CRN}, including support for the 
SBML. Poincaré and SimBio are developed as pure Python
packages enabling users to easily extend their simulation capabilities
by writing new or leveraging other Python packages. Moreover, this does
not compromise the performance, as code can be Just-In-Time compiled
with Numba. Our benchmark tests using curated models from the BioModels
repository demonstrate that these tools may provide a potentially
superior performance advantage compared to other existing tools.
Additionally, to ensure a user-friendly experience, our packages use
standard typed modern Python syntax that provides a seamless integration
with \acp{IDE}. Our Python-centric approach
significantly enhances code analysis, error detection, and refactoring
capabilities, positioning Poincaré and SimBio as valuable tools for the
modelling community.
\end{abstract}

>>>>

\usepackage{acronym}
\acrodef{CRN}[CRN]{chemical reaction network}
\acrodef{DSL}[DSL]{domain-specific language}
\acrodef{GPU}[GPU]{graphical processing unit}
\acrodef{GUI}[GUI]{graphical user interface}
\acrodef{IDE}[IDE]{integrated development environment}
\acrodef{JIT}[JIT]{just-in-time}
\acrodef{ODE}[ODE]{ordinary differential equation}
\acrodef{PyPI}[PyPI]{Python package index}
\acrodef{RHS}[RHS]{right-hand side}
\acrodef{SBML}[SBML]{Systems Biology Markup Language}
\acrodef{SDE}[SDE]{stochastic differential equation}
\acrodef{TPU}[TPU]{tensor processing unit}

@@

\begin{abstract}
\Acfp{CRN} play a pivotal role in diverse fields
such as systems biology, biochemistry, chemical engineering, and epidemiology.
High-level modelling of \acp{CRN} enables various simulation approaches,
including deterministic and stochastic methods.
However,
existing Python tools for \ac{CRN} modelling typically wrap external C/C++ libraries for modelling and simulation,
limiting their extensibility and integration with the broader Python ecosystem.
In response, we developed Poincaré and SimBio,
two novel Python packages for the definition and simulation of dynamical systems and \acp{CRN}.
Poincaré serves as a foundation for dynamical systems modelling,
while SimBio extends this functionality to \acp{CRN},
including support for the \ac{SBML}.
Poincaré and SimBio are developed as pure Python packages
enabling users to easily extend their simulation capabilities
by writing new or leveraging other Python packages.
Moreover, this does not compromise the performance,
as code can be \ac{JIT} compiled with Numba.
Our benchmark tests using curated models from the BioModels repository
demonstrate that these tools may provide a potentially
superior performance advantage compared to other existing tools.
Additionally, to ensure a user-friendly experience,
our packages use standard typed modern Python syntax that provides a seamless integration with \acp{IDE}.
Our Python-centric approach significantly enhances code analysis, error detection, and refactoring capabilities,
positioning Poincaré and SimBio as valuable tools for the modelling community.
\end{abstract}
